%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Topological Data Analysis \& Image Classification
% Version 1.0 (20211125)
%
% Author: River Reger
% e-mail: river.reger@gmail.com
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------
\documentclass[10pt]{beamer}
\mode<presentation> {
\usetheme{Frankfurt}
\usecolortheme{beaver}
\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides
}
\include{Parameters}
%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------
\title[TDA for Image Classification]{Topological Data Analysis (TDA) for Image Classification}
\subtitle{Virtual}
\author[River Reger]{River Reger \\ \href{mailto:river.reger@gmail.com}{river.reger@gmail.com}}
\date{\small Technical Presentation \\ 2021 November 29} % Date, can be changed to a custom date

\begin{document}

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

\begin{frame}
\frametitle{Overview}
\tableofcontents
\end{frame}
%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------
\input{Intro_TDA}
\input{Iris_Data}
\input{Digits_Data}
\input{Cancer_Data}


%================================================
\section{Conclusions \& Questions}
%================================================
	\begin{frame}
			\frametitle{Conclusions}
			\begin{itemize}
				\item Traditional Data Analysis has seen great progress over the past decade due to the copious amounts of data
				available paired with ever increasing availability of high performance computing resources.
				\item TDA offers new and rigorous tools from mathematics for analyzing datasets at a global scale.
				\item As seen in the simple dataset examples, differences in data can be explained by the inherent homology information that is encoded within the dataset.
				\item This is a unique tool that can be added to data scientists' toolboxes for more detailed analysis of the underlying shape of data.
				\item The bottleneck metric must be used with caution as an actual scoring metric.
				\item The analysis from TDA tends to be less quantitative and more qualitative.
			\end{itemize}
	\end{frame}
		
	\begin{frame}
		\frametitle{Future Work}
		
		\begin{itemize}
			\item Since we can extract vectors and images as topological information, more work is needed on the practical meaningfulness of these features under traditional techniques including:
				\begin{itemize}
					\item Convolutional Neural Networks (CNNs) on Persistence Images
					\item Image Segmentation (noise/signal separation) on PIs.
					\item Support Vector Machines (SVMs) and other classical ML algorithms using persistence diagrams as vector sets.
				\end{itemize}
			\item There is a large gap in academia and practice in modalities beyond RGB images or small numerical vectors. Particular areas of interest could include:
				\begin{itemize}
					\item Non-image based data (radar waveforms, GDELT text-based data, sentiment analysis, etc.)
					\item Imagery: SAR (especially 3D SAR), HSI, MWIR, LWIR, Lidar
					\item Military messaging systems (Link-16 messages), scenario data (laydown parameters)
					\item Cybersecurity threat analysis
				\end{itemize}
		\end{itemize}
	\end{frame}

	\begin{frame}
		\Huge{\centerline{Questions?}}
	\end{frame}
\end{document} 